Political Polarization, Public Trust, and Healthcare Disparities: Unraveling COVID-19's Impact and Future Preparedness

### 2024-02-15 outputs/paper/paper.qmd
fixed format

# Print the sample table
kable(vote_share_sample, 
      format = "markdown", 
      col.names = c("State Name", "County FIPS", "County Name", "Votes GOP", "Votes DEM", "Total Votes", "Difference", "Percentage GOP", "Percentage DEM", "Percentage Point Difference")
)

>>>>

# Print the sample table
kable(vote_share_sample, 
      format = "markdown", 
      col.names = c("State Name", "County  FIPS", "County Name", "Votes GOP", "Votes DEM", "Total Votes", "Differ- ence", "Percent- age GOP", "Percent- age DEM", "Percentage Point Difference")
)
